Using Visual Analytics to Explain\\[1ex] Black-Box Machine Learning

### 2018-04-03 tex/introduction/motivation.tex
citations

The above examples illustrate the need for human understanding and supervision in machine learning.
However, those cases required intricate understanding of the used machine learning models and are not easily generalized to other techniques.
For example, in the case of Caruana~\etal\cite{Caruana:2015:IMH:2783258.2788613}, the incorrect correct result was easily identified since the authors used a special, intelligible, model.
However, not all models used in machine learning are, or even attempt to be, easily interpretable by human experts.
To counteract this, visual analytics has been successfully used to visualize machine learning processes in order to understand and gain insights into predictive models \todo{cite vis papers last year}. Visual analytics is the area of studying interactive graphical representations of abstract information with the help of computational and statistical procedures, in order to effectively analyze complex data. With regards to understanding the decision making of predictive machine learning models, there are two main strategies: white-box and black-box analysis \cite{class_signatures}.

>>>>

The above examples illustrate the need for human understanding and supervision in machine learning.
However, those cases required intricate understanding of the used machine learning models and are not easily generalized to other techniques.
For example, in the case of Caruana~\etal\cite{Caruana:2015:IMH:2783258.2788613}, the incorrect correct result was easily identified since the authors used a special, intelligible, model.
However, not all models used in machine learning are, or even attempt to be, easily interpretable by human experts.
To counteract this, visual analytics has been successfully used to visualize machine learning processes in order to understand and gain insights into machine learning models~\cite{DBLP:journals/corr/StrobeltGHPR16,DBLP:journals/corr/abs-1710-06501,2017arXiv170401942K,DBLP:journals/corr/abs-1710-10777,8019879,8019872,DBLP:journals/tvcg/LiuXLWWZ18,8019878}. Visual analytics is the area of studying interactive graphical representations of abstract information with the help of computational and statistical procedures, in order to effectively analyze complex data. With regards to understanding the decision making of predictive machine learning models, there are two main strategies: white-box and black-box analysis \cite{class_signatures}.
